Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-16 paper/ms.tex
aas resubmit stage
AAS accepted

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{August 6, 2020}
\revised{September 7, 2020}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

@@

The Rossiter-McLaughlin approach is more likely to yield short-term
success than a direct mass measurement because of the RV noise
expected to be induced by stellar rotation.  The photometric amplitude
induced by starspots on \tn\ is $\approx 2\%$.  The spot-induced RV
variation expected over the course of the $\approx 3\,{\rm d}$
rotation period can be estimated by multiplying the photometric
amplitude and spectroscopic equatorial velocity.  This gives
$\sigma_{\rm RV,rot} \approx 300\,{\rm m\,s}^{-1}$, and is consistent
with the scatter we observe in our radial velocities from FEROS.
Detecting a planet's Keplerian motion in this regime is challenging,
and requires a significant amount of data and care in signal
extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
measurement avoids the majority of this issue because the transit
occurs over a much shorter duration than a single stellar rotation
period.

@@

\added{The authors thank K.~Anderson for fruitful discussions, and
T.~Guillot for contributions to the ASTEP project.  We are also
grateful to the anonymous referee for their constructive comments and
suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{August 6, 2020}
\revised{September 6, 2020}
\accepted{September 16, 2020}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

@@

The Rossiter-McLaughlin approach is more likely to yield short-term
success than a direct mass measurement because of the RV noise
expected to be induced by stellar rotation.  The photometric amplitude
induced by starspots on \tn\ is $\approx 2\%$.  The spot-induced RV
variation expected over the course of the $\approx 3\,{\rm d}$
rotation period can be estimated by multiplying the photometric
amplitude and spectroscopic equatorial velocity.  This gives
$\sigma_{\rm RV,rot} \approx 300\,{\rm m\,s}^{-1}$, and is consistent
with the scatter we observe in our radial velocities from FEROS.
Detecting a planet's Keplerian motion in this regime is challenging,
and requires a significant amount of data and care in signal
extraction \citep{barragan_radial_2019,stefansson_k2-25_2020}.  The
Rossiter-McLaughlin measurement avoids the majority of this issue
because the transit occurs over a much shorter duration than a single
stellar rotation period.

@@

\added{The authors thank K.~Anderson for fruitful discussions, and are
also grateful to the anonymous referee for their constructive comments
and suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%
